title: "Intro"
author: "MK Larson"
date: "December 2, 2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, message = FALSE, include=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")

library(roller)
```

## Rolling a Dice
This package simulates tossing a coin(or device), a specific number of times. From there, the relative frequencies are calculated and a plot of the series is displayed.

##Creating the Device
To create your own device, you must create the dice object. To do this, use the function device().

```{r}
new_device <- device()
new_device
```

By default, 'device()' will create a fair coin with standard sides of 1 and 2, and probabilities of 0.5.
To change this, you must use the arguments 'sides' and 'prob'
```{r}
load_dice <- device(sides = c("heads", "tails"), prob = c(0.9, 0.1))
```
#Roll the Device
Once the device is created, we then have to roll it. The function "roll()" will execute this, given a specific number of times.
The output is an object of class "roll", and will contain the vector "rolls"
```{r}
roll25 <- roll(new_device, times = 20)
roll25
```

The 'summary()' function will return a list with the data frame containing the counts and frequencies.

```{r}
summary25 <- summary(roll25)
summary25
```

The function 'plot()' will produce a barchart of the relative frequencies for each side.
```{r}
plot(roll25)
```

The `"["` (extraction) method allows us to extract individual rolls.
```{r}
roll25[10]
```

The `"[<-" method allows us to replace the value of a roll.
```{r}
roll25[11] <- 5
roll25[11]
roll25[11] <- 1
roll25[11]
```

the `"+"` method allows us to add rolls to an already rolled object.
```{r}
roll45 <- roll25 + 20
summary(roll45)
```
